---
title: "Lefse analysis in R"
output: html_document
---

```{r setup, include=FALSE}
# Plotting lefse data

library(ggplot2)
```
# also ran ggthemr WP1 cols to get correct colours per tmt

# Using lefse_summary file output from mothur, trim data to 
# p < 0.01 & then choose some cut off of LDA vals. I used LDA > 3.5

# in excel i had ordered this data accroding to treatment (ie sample day)
# and then within those groupings I ordered according to LDA score (big to small). 
# makes final plot pretier. Probably a very simple way to do this in R
# but I didnt have time to figure out how :?

# read in data. 
```{r}
LFKA <- read.table("analysis.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.opti_mcc.0.03.AvsKexcel35.txt", header = TRUE, sep="\t" )
LFDJ <- read.table("analysis.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.opti_mcc.0.03.DvsJexcel35.txt", header = TRUE, sep="\t" )
    ### Added dashes in 4th and 5th columns of .txt files
  #### in excel, I got rid of all rows with dashes (non-significant) OTUs
head(LFKA)
head(LFDJ)
```


# set order to be by order of OTUs in original file

```{r}
LFKA$OTU <- factor(LFKA$OTU, levels = LFKA$OTU)
LFDJ$OTU <- factor(LFDJ$OTU, levels = LFDJ$OTU)
```

# in fact, i want rev of this as make plot easier to interpret

```{r}
LFKA$OTU <- factor(LFKA$OTU, levels = rev(LFKA$OTU))
LFDJ$OTU <- factor(LFDJ$OTU, levels = rev(LFDJ$OTU))

ka <- ggplot(LFKA, aes(x=OTU, y=LDA, fill=Class), show_guide=FALSE) + 
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() # flip it 90
dj <- ggplot(LFDJ, aes(x=OTU, y=LDA, fill=Class), show_guide=FALSE) + 
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() # flip it 90

```


# Replace OTU### with tax info:
# using concatenate in excel to add "" , faster, make this string of 
# tax info matching OTU id. Name this:

```{r}
## Have to make a vector with the names of the taxa matching each significant OTU

head(tax.clean)
myLabscd <- tax.clean
```

# then add these labels to the to plot 
```{r}
KAL <- ka + scale_x_discrete(labels=myLabscd$Family, position = "top")
DJL <- dj + scale_x_discrete(labels=myLabscd$Family, position = "top")
```


## change font colour size etc
```{r}
k = KAL + theme_gray() +
  theme(axis.text.x=element_text(hjust=10, size=8, vjust=0.1, colour="black")) +
  theme(axis.text.y=element_text(hjust=10, size=15, vjust=0.1, colour="black")) +
  theme(axis.title.x=element_text(size=8, colour="black")) +
  theme(axis.title.y=element_text(size=8, colour="black")) + 
  labs(fill="Treatment Type\n") +
  theme(legend.title =element_text(size=12, colour="black")) +
  theme(legend.text = element_text(size=14, colour="black")) +
  guides(fill = guide_legend(override.aes = list(size=3)))

d = DJL + theme_gray() +
  theme(axis.text.x=element_text(hjust=10, size=8, vjust=0.1, colour="black")) +
  theme(axis.text.y=element_text(hjust=10, size=14, vjust=0.1, colour="black")) +
  theme(axis.title.x=element_text(size=8, colour="black")) +
  theme(axis.title.y=element_text(size=8, colour="black")) + 
  labs(fill="Strain\n") +
  theme(legend.title =element_text(size=12, colour="black")) +
  theme(legend.text = element_text(size=14, colour="black")) +
  guides(fill = guide_legend(override.aes = list(size=3)))

plot(k + 
       labs(title = "Family Differences between Ace (control) and Kan (antibiotic) Treatments (LDA > 3.5)", size=4))
plot(d +
       labs(title = "Family Differences between Danville (R) and Jwax (S) Strains (LDA > 3.5)", size=4)) 
```


# print & save as pdf 


